### 2019-08-22 README.Rmd
docs are built by ropensci directly now, so drop pkgdown

- [A Brief Introduction to RNeXML](https://ropensci.github.com/RNeXML/articles/intro)
- [RNeXML: A Package for Reading and Writing Richly Annotated Phylogenetic, Character, and Trait Data in R](https://ropensci.github.com/RNeXML/articles/manuscript.pdf) (published in MEE).
- [Handling Metadata in RNeXML](https://ropensci.github.com/RNeXML/articles/metadata)
- [The `nexml` S4 Object](https://ropensci.github.com/RNeXML/articles/S4)
- [Semantic data & SPARQL with RNeXML](https://ropensci.github.com/RNeXML/articles/SPARQL)
- [Extending NeXML: an example based on simmap](https://ropensci.github.com/RNeXML/articles/simmap)

>>>>

- [A Brief Introduction to RNeXML](https://docs.ropensci.org/RNeXML/articles/intro)
- [RNeXML: A Package for Reading and Writing Richly Annotated Phylogenetic, Character, and Trait Data in R](https://docs.ropensci.org/RNeXML/articles/manuscript.pdf) (published in MEE).
- [Handling Metadata in RNeXML](https://docs.ropensci.org/RNeXML/articles/metadata)
- [The `nexml` S4 Object](https://docs.ropensci.org/RNeXML/articles/S4)
- [Semantic data & SPARQL with RNeXML](https://docs.ropensci.org/RNeXML/articles/sparql)
- [Extending NeXML: an example based on simmap](https://docs.ropensci.org/RNeXML/articles/simmap)
